\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{microtype}
\usepackage{amsmath,amssymb,mathtools}
\usepackage{booktabs,longtable,array,tabularx}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{caption}

\geometry{margin=25mm,headheight=15pt}
\definecolor{navy}{HTML}{17324D}
\definecolor{blue}{HTML}{2563A6}
\definecolor{teal}{HTML}{147D73}
\definecolor{red}{HTML}{A53B3B}
\definecolor{amber}{HTML}{A66518}
\definecolor{light}{HTML}{F3F6F8}
\definecolor{mid}{HTML}{D5DEE5}
\definecolor{textgray}{HTML}{4B5563}

\hypersetup{
  colorlinks=true,
  linkcolor=navy,
  urlcolor=blue,
  citecolor=teal,
  pdftitle={Modern Bazaar: A Quantitative Market Intelligence System},
  pdfauthor={Pedro Silva}
}

\pagestyle{fancy}
\fancyhf{}
\lhead{\textcolor{textgray}{Modern Bazaar}}
\rhead{\textcolor{textgray}{Quantitative System Specification}}
\cfoot{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.65em}
\setlist[itemize]{leftmargin=1.5em,itemsep=0.25em,topsep=0.3em}
\setlist[enumerate]{leftmargin=1.6em,itemsep=0.25em,topsep=0.3em}
\captionsetup{font=small,labelfont=bf}

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\clip}[1]{\min\!\left(1,\max(0,#1)\right)}
\newcommand{\halfSat}[2]{\frac{#1}{#1+#2}}
\newcommand{\quality}[1]{\textcolor{teal}{#1}}
\newcommand{\risk}[1]{\textcolor{red}{#1}}
\newcommand{\implementation}[1]{%
  \vspace{0.2em}\noindent
  \colorbox{light}{\parbox{0.95\linewidth}{\textbf{Implementation note.} #1}}
  \vspace{0.2em}}

\begin{document}
\pagenumbering{gobble}

\begin{titlepage}
  \centering
  \vspace*{24mm}
  {\color{navy}\rule{\textwidth}{1.2pt}}\\[12mm]
  {\Huge\bfseries\color{navy} Modern Bazaar\\[4mm]}
  {\LARGE A Quantitative Market Intelligence System\\[4mm]}
  {\large Data Engineering, Market Metrics, Flipping, Risk, and Manipulation Ranking}
  \\[12mm]
  {\color{navy}\rule{\textwidth}{1.2pt}}
  \vfill
  \begin{tabular}{rl}
    \textbf{Author:} & Pedro Silva\\
    \textbf{Document type:} & Quantitative system specification\\
    \textbf{System version:} & Repository state as of 10 July 2026\\
    \textbf{Status:} & Implemented system with documented limitations
  \end{tabular}
  \vfill
  \begin{minipage}{0.86\textwidth}
  \small\color{textgray}
  This document explains the implemented Modern Bazaar system in precise but readable
  terms. Equations describe the software as it exists; they are not promises of profit.
  Market conditions, hidden order-book depth, competing players, and game mechanics can
  cause realized outcomes to differ materially from model estimates.
  \end{minipage}
\end{titlepage}

\pagenumbering{roman}
\tableofcontents
\clearpage
\pagenumbering{arabic}

\section{Executive Summary}

Modern Bazaar is a market-intelligence platform for the Hypixel SkyBlock Bazaar. It turns
frequent public API observations into a compact historical record, rolling liquidity
metrics, risk estimates, and ranked trading opportunities. Its quantitative core answers
two different questions:

\begin{enumerate}
  \item \textbf{Flipping:} can a trader repeatedly buy at the current bid, sell at the
  current ask, and earn an attractive risk-adjusted profit within a chosen time horizon?
  \item \textbf{Market manipulation analysis:} can the visible and estimated sell side be
  acquired within budget, and does historical order flow suggest that an inflated position
  could be exited before competing supply overwhelms it?
\end{enumerate}

The system is deliberately empirical. Live prices describe the current opportunity;
hourly summaries describe how the market normally behaves; rolling averages reduce noise;
and scoring functions combine profitability with liquidity, competition, market control,
attention, and adverse sell pressure.

The default manipulation model, called \emph{Balanced}, is the most important recent
development. It combines the bidder-attraction behavior of the Attention model with the
sell-pressure discipline learned from the Overclocker model. Its design reflects a practical
observation: attention is valuable only when a position can survive the sellers attracted by
the same price movement.

\section{System Boundary and Architecture}

The production system contains five cooperating layers:

\begin{center}
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash\bfseries}p{0.18\textwidth}X}
\toprule
Layer & Responsibility\\
\midrule
Hypixel API & Supplies current Bazaar products, prices, aggregate volumes, order counts,
and the visible top of each order book.\\
Spring Boot core & Polls, validates, deduplicates, stores, compacts, aggregates, scores,
and exposes REST endpoints.\\
PostgreSQL & Stores product metadata, raw snapshots, visible order-book entries, hourly
summaries, retained hour points, and precomputed finance metrics.\\
Next.js dashboard & Presents searchable market data, strategy filters, ranked opportunities,
and detailed plans.\\
Operations stack & Caddy terminates TLS and routes traffic; Prometheus collects application
and database metrics; Grafana presents operational dashboards.\\
\bottomrule
\end{tabularx}
\end{center}

In production, the core services share an internal Docker network. Only Caddy binds public
ports. It routes the API, Grafana, and Prometheus subdomains to their internal services.
PostgreSQL is not directly exposed to the Internet.

\subsection{Data-flow overview}

The principal data path is:

\begin{align*}
\text{Hypixel API}&\longrightarrow \text{snapshots}
\longrightarrow \text{hourly summaries and points}\\
&\longrightarrow \text{rolling metrics}
\longrightarrow \text{strategy scores}
\longrightarrow \text{dashboard}.
\end{align*}

This separation is useful quantitatively. A live snapshot determines executable-looking
prices and visible depth, while historical summaries determine whether those prices are
supported by normal market behavior.

\section{Market Notation}

Hypixel's API naming can be unintuitive, so this document uses economic notation.

\begin{longtable}{p{0.18\textwidth}p{0.23\textwidth}p{0.50\textwidth}}
\toprule
Symbol & System field & Meaning\\
\midrule
\endhead
$a_t$ & instant buy price & Lowest standing sell-order price: the approximate price paid
to buy immediately. This is the market ask.\\
$b_t$ & instant sell price & Highest standing buy-order price: the approximate price received
when selling immediately. This is the market bid.\\
$s_t=a_t-b_t$ & spread & Gross quoted spread per unit.\\
$\rho_t=s_t/b_t$ & spread percentage & Spread relative to the approximate buy-order entry price.\\
$V_t^B,V_t^S$ & buy/sell volume & Current aggregate unit depth reported by the API.\\
$N_t^B,N_t^S$ & active buy/sell orders & Current number of standing orders on each side.\\
$M_t^B,M_t^S$ & moving-week volumes & Rolling seven-day cumulative activity fields used to
infer executed units between snapshots.\\
$\tau$ & tax rate & Fraction removed from sale proceeds; default $\tau=0.01125$.\\
\bottomrule
\end{longtable}

All prices are in coins and all flow metrics are normalized to units or events per hour.

\section{Ingestion and Persistence}

\subsection{Polling and deduplication}

The core polls the Bazaar endpoint every 60 seconds by default. If the API reports timestamp
$T$, the system persists at most one snapshot for each pair

\begin{equation}
(\text{productId},T).
\end{equation}

This avoids storing repeated scheduler observations when Hypixel has not published a new
market state. Products absent from the local catalog are inserted before their snapshots.
Snapshots are written in batches of 50 to bound persistence-context memory.

For every product, a snapshot stores prices, reported volume and moving-week statistics,
active order counts, weighted two-percent prices, and the visible buy and sell order entries
returned by the API.

\subsection{Hourly compaction}

Every five minutes, a compaction job checks the oldest unprocessed snapshot. Once a complete
one-hour interval plus a two-minute grace period exists, snapshots in that interval are
reduced to an hourly summary and a selected set of representative points.

Let the snapshots in hour $h$ be ordered as $x_0,x_1,\ldots,x_n$. The summary records open,
close, minimum, and maximum prices, plus order-flow and execution proxies. Representative
points are retained when there is a sufficiently large time gap or price movement, preserving
chart shape without retaining every raw observation forever.

The configured price-movement threshold is $0.2\%$, and the default maximum gap between kept
points is five minutes. Conceptually, a point is retained when

\begin{equation}
\left|\frac{p_i-p_k}{p_k}\right|\ge 0.002
\quad\text{or}\quad
t_i-t_k\ge 5\text{ minutes},
\end{equation}

where $k$ is the previously retained observation.

\subsection{Retention}

At application startup and daily at 03:00, the retention job deletes snapshots, hour points,
and hourly summaries older than the configured retention interval. The repository documents
a 45-day operational target, while the code-level default is 30 days if configuration is
absent. Production behavior therefore depends on the active profile configuration.

The storage policy is a compromise:

\begin{itemize}
  \item detailed recent observations support debugging and short-term analysis;
  \item hourly summaries preserve the variables needed by current scorers;
  \item representative hour points preserve visual price paths;
  \item bounded retention prevents indefinite database growth.
\end{itemize}

\section{Hourly Market Metrics}

\subsection{Order-count activity proxies}

For consecutive snapshots $i-1$ and $i$, increases in active order count are treated as
newly created orders:

\begin{align}
C_h^B &= \sum_i \max(0,N_i^B-N_{i-1}^B),\\
C_h^S &= \sum_i \max(0,N_i^S-N_{i-1}^S).
\end{align}

These are \emph{observed net-increase events}, not a perfect event log. If ten orders are
created while ten existing orders disappear between polls, the active count does not change
and those creations are unobservable.

When the order count rises, the implementation estimates newly added units using the absolute
change in aggregate volume:

\begin{align}
A_h^B &= \sum_{i:N_i^B>N_{i-1}^B}\left|V_i^B-V_{i-1}^B\right|,\\
A_h^S &= \sum_{i:N_i^S>N_{i-1}^S}\left|V_i^S-V_{i-1}^S\right|.
\end{align}

These variables are useful pressure proxies, but executions and cancellations occurring in
the same polling interval can distort them.

\subsection{Insta-trade flow}

Positive changes in the rolling seven-day fields estimate executed flow:

\begin{align}
I_h^{\mathrm{sold}} &= \sum_i \max(0,M_i^B-M_{i-1}^B),\\
I_h^{\mathrm{bought}} &= \sum_i \max(0,M_i^S-M_{i-1}^S).
\end{align}

$I_h^{\mathrm{sold}}$ represents units players insta-sold into standing buy orders.
$I_h^{\mathrm{bought}}$ represents units players insta-bought from standing sell orders.

\subsection{Top-bid chase behavior}

The system measures how often the best bid rises:

\begin{align}
U_h &= \sum_i \mathbf{1}\{b_i>b_{i-1}\},\\
\Delta_h^+ &= \sum_i \max(0,b_i-b_{i-1}).
\end{align}

$U_h$ is the number of upward moves and $\Delta_h^+$ is their cumulative coin magnitude.
The current Balanced formula uses $U_h$ but exposes $\Delta_h^+$ only diagnostically.

\subsection{Rolling arithmetic averages}

For metric $X_h$ and a window containing $n$ available hourly observations,

\begin{equation}
\bar X_n=\frac{1}{n}\sum_{j=1}^{n}X_{h-j+1}.
\end{equation}

The system precomputes windows of 1, 6, and 48 hours every 60 minutes. If fewer than the
requested number of observations exist, the mean uses the available observations. Thus the
stored \code{windowHours} may represent a target while the observation count represents the
actual sample size.

\implementation{The manipulation scorer currently uses the 48-hour averages. The flipping
scorer uses all three windows and selects the smallest positive flow estimate, producing a
conservative liquidity estimate.}

\section{Shared Price-Risk Model}

The risk toolkit measures whether current prices are unusually far from two references:
the latest weighted two-percent price and the historical mean closing price.

For value $v$ and valid reference $r>0$, define relative deviation

\begin{equation}
d(v,r)=\frac{|v-r|}{r}.
\end{equation}

For each side of the book, the system takes the largest available deviation:

\begin{align}
d_B &= \max\{d(a_t,a_t^{2\%}),d(a_t,\bar a^{\mathrm{close}})\},\\
d_S &= \max\{d(b_t,b_t^{2\%}),d(b_t,\bar b^{\mathrm{close}})\}.
\end{align}

It also measures a reference shock between the weighted and historical values:

\begin{equation}
q=\max\left\{d(a_t^{2\%},\bar a^{\mathrm{close}}),
d(b_t^{2\%},\bar b^{\mathrm{close}})\right\}.
\end{equation}

The normalized risk score is

\begin{equation}
R=\clip{\max\left(\frac{\max(d_B,d_S)}{0.20},\frac{q}{0.25}\right)}.
\end{equation}

The market is flagged as likely atypical or already manipulated if

\begin{equation}
\max(d_B,d_S)\ge0.15
\quad\lor\quad q\ge0.12
\quad\lor\quad R\ge0.85.
\end{equation}

This is an anomaly heuristic, not a causal classifier: it detects unusual price regimes but
cannot prove why they occurred.

\section{Bazaar Flipping Model}

\subsection{Liquidity selection}

Let $D_w$ and $S_w$ denote average insta-bought and insta-sold units for window
$w\in\{1,6,48\}$ hours. The selected demand and supply are the smallest positive values:

\begin{equation}
D=\min{}^+(D_1,D_6,D_{48}),\qquad
S=\min{}^+(S_1,S_6,S_{48}).
\end{equation}

This avoids projecting an unusually active short period across the whole trading horizon.
Executable throughput is constrained by both sides:

\begin{equation}
Q=\min(D,S).
\end{equation}

Markets with $Q<1$ unit/hour receive score zero.

\subsection{Budget, horizon, and competition}

For budget $B$ and horizon $H$, affordable units per hour are

\begin{equation}
Q_B=\left\lfloor\frac{B}{b_tH}\right\rfloor,
\end{equation}

and planned capacity is $Q_P=\min(Q,Q_B)$ when a budget is supplied.

Let $C_B$ and $C_S$ be average created-order proxies. Define

\begin{align}
C_{\max}&=\max(C_B,C_S),& C_{\min}&=\min(C_B,C_S),\\
\eta&=\frac{C_{\max}-C_{\min}}{C_{\max}+1},&
C_{\mathrm{eff}}&=C_{\max}(1+0.5\eta).
\end{align}

The side-balance adjustment is approximately

\begin{equation}
L=\min\left(1,\frac{S}{D+1}\right),
\end{equation}

with explicit edge handling for absent demand or supply. With competition coefficient
$\kappa$, suggested units per hour become

\begin{equation}
Q_{\mathrm{sugg}}=
\frac{\min(Q_PH,QHL)}{H\max(10^{-6},1+\kappa C_{\mathrm{eff}})}.
\end{equation}

\subsection{Profit and score}

The current implementation treats the gross spread as the pre-risk unit margin and discounts
it by risk:

\begin{align}
\pi_u &= s_t(1-R),\\
\Pi_h &= \pi_u Q_{\mathrm{sugg}}.
\end{align}

Define

\begin{align}
P &= \log_{10}(\Pi_h+1),\\
G &= \min(0.8,12\rho_t),\\
P_R &= 0.1R,\\
P_C &= \min(0.10,0.0007C_{\mathrm{eff}}),\\
L_Q &= \min(1,Q/8).
\end{align}

The final flipping score is

\begin{equation}
\boxed{S_{\mathrm{flip}}=P(1+G)(1-P_R)(1-P_C)L_Q.}
\end{equation}

Estimated fill times for the suggested quantity $Q_{\mathrm{sugg}}H$ are

\begin{align}
T_{\mathrm{buy}}&=\frac{Q_{\mathrm{sugg}}H}{S},&
T_{\mathrm{sell}}&=\frac{Q_{\mathrm{sugg}}H}{D},&
T_{\mathrm{total}}&=T_{\mathrm{buy}}+T_{\mathrm{sell}}.
\end{align}

\risk{Important: the implemented flipping margin does not explicitly subtract Bazaar tax.
The score is therefore best interpreted as a comparative ranking signal, not an accounting
statement of guaranteed net profit.}

\section{Manipulation Planning Model}

This section documents the model used to rank markets that appear cornerable. It describes
the system's analytical behavior; actual market actions remain exposed to hidden liquidity,
competing supply, execution delay, game rules, and substantial loss risk.

\subsection{Estimating total sell-side depth}

The API exposes only the top portion of the order book. Let

\begin{itemize}
  \item $U_v$ be visible sell units,
  \item $K_v$ be visible sell orders,
  \item $K$ be the API's total active sell-order count,
  \item $V^S$ be aggregate sell volume,
  \item $C_v$ be cost of all visible units,
  \item $p_{\max}$ be the worst visible ask.
\end{itemize}

Missing orders are $K_m=\max(0,K-K_v)$. If $K_v>0$, units are extrapolated as

\begin{equation}
\widehat U=\max\left(U_v,
U_v+K_m\frac{U_v}{K_v},
V^S\right).
\end{equation}

The base hidden-unit price is conservatively selected as

\begin{equation}
p_h^{(0)}=\max\left(\frac{C_v}{U_v},p_{\max}\right).
\end{equation}

It receives a premium based on the proportion of hidden orders:

\begin{align}
r_h&=\min\left(1,\frac{K_m}{K_v}\right),\\
p_h&=p_h^{(0)}(1+0.25r_h).
\end{align}

The estimated corner cost is therefore

\begin{equation}
\boxed{\widehat C=C_v+\max(0,\widehat U-U_v)p_h.}
\end{equation}

This extrapolation deliberately charges hidden units at no less than the worst visible price.
It cannot recover the true hidden distribution, but it is safer than assuming every hidden
unit trades at the visible average.

\subsection{Break-even, target, and projected profit}

Average acquisition cost is

\begin{equation}
\bar c=\frac{\widehat C}{\widehat U}.
\end{equation}

With sale tax $\tau$, the break-even resell price is

\begin{equation}
p_{\mathrm{BE}}=\frac{\bar c}{1-\tau}.
\end{equation}

For selected return multiplier $r\ge1$ and sell-wall multiplier $w>1$,

\begin{align}
p_T&=rp_{\mathrm{BE}},\\
p_W&=wp_T.
\end{align}

The projected net profit per unit and total projected profit are

\begin{align}
\pi_u&=p_T(1-\tau)-\bar c,\\
\Pi&=\widehat U\pi_u.
\end{align}

Because $p_T=r\bar c/(1-\tau)$, this simplifies to

\begin{equation}
\Pi=\widehat C(r-1).
\end{equation}

This identity is important: for fixed $r$, projected profit is proportional to capital
deployed. The later quality terms must therefore prevent large but operationally poor markets
from dominating the ranking.

\subsection{Required bid movement and exit time}

Starting from current best bid $b_t$, required doubling steps are

\begin{equation}
n_2=\left\lceil\log_2\left(\frac{p_T}{b_t}\right)\right\rceil_+,
\end{equation}

where the value is zero when $p_T\le b_t$.

Let $E=\bar A^B$ be average newly added buy-order units/hour. The estimated exit time is

\begin{equation}
T_E=\frac{\widehat U}{E}.
\end{equation}

Let $A^S$ be added sell-order units/hour and $I^{\mathrm{sold}}$ be insta-sold units/hour.
The adverse unit-pressure estimate is

\begin{equation}
P_S=A^S+I^{\mathrm{sold}}.
\end{equation}

The exit estimate assumes historical new buy-order units are potentially available to absorb
the position. It does not guarantee that those orders appear above the required exit price or
remain in place.

\section{Common Manipulation Score}

Before the versioned order-flow formula is applied, all manipulation models share the same
hard gates and broad market-quality terms.

\subsection{Hard gates}

An opportunity receives score zero if any of the following holds:

\begin{align*}
\Pi&\le0,& D&<1\text{ unit/hour},& E&\le0,\\
n_2&>6,& R&\ge0.85,& T_E&>24\text{ hours}.
\end{align*}

The list endpoint adds practical filters for budget, maximum units, current item price,
demand/supply ratio, and minimum profit. Craftable and NPC-buyable products on maintained
exclusion lists are removed. Higher-tier enchantments are removed when two lower-tier units
can be combined more cheaply than the proposed target price.

With budget $B$, the default minimum-profit floor is

\begin{equation}
\Pi_{\min}=\min(0.10B,50{,}000{,}000).
\end{equation}

The default current item-price cap is 1.5 million coins.

\subsection{Base quality factors}

Projected profit is compressed logarithmically:

\begin{equation}
Q_\Pi=\log_{10}(\Pi+1).
\end{equation}

Corner-size quality favors operationally manageable inventories:

\begin{equation}
Q_U=\frac{10{,}000}{10{,}000+\widehat U}.
\end{equation}

Let $D$ be insta-buy demand, $S$ insta-sell supply, and

\begin{equation}
z=\begin{cases}
\min(5,D/S),&S>0,\\
5,&S=0,D>0,\\
0,&D=S=0.
\end{cases}
\end{equation}

Demand quality is

\begin{equation}
Q_D=\frac{D}{D+10}\left(0.35+0.65\frac{z}{z+3}\right).
\end{equation}

Exit-speed quality is

\begin{equation}
Q_T=\frac{3}{3+T_E}.
\end{equation}

Bid-climb realism and anomaly survival are

\begin{align}
Q_2&=\exp(-n_2/2.5),\\
Q_R&=\clip{1-0.9R}.
\end{align}

\subsection{Standing market-control quality}

Let active sell orders, active buy orders, sell units, and buy units be
$N^S,N^B,V^S,V^B$. Define

\begin{align}
t_{SO}&=\frac{60}{60+N^S},&
t_{SV}&=\frac{50{,}000}{50{,}000+V^S},\\
d_{BO}&=\frac{N^B}{N^B+120},&
d_{BV}&=\frac{V^B}{V^B+50{,}000},\\
i_O&=\frac{N^B+1}{N^B+N^S+2},&
i_V&=\frac{V^B+1}{V^B+V^S+2}.
\end{align}

Then

\begin{equation}
Q_M=0.15+0.85(0.25t_{SO}+0.25t_{SV}+0.20d_{BO}
+0.15d_{BV}+0.10i_O+0.05i_V).
\end{equation}

This rewards thin sell-side control and substantial buyer-side depth without allowing market
control alone to reduce the score all the way to zero.

\section{Order-Flow Signals}

For readability, define the half-saturation transform

\begin{equation}
H(x;k)=\frac{x}{x+k}
\end{equation}

and the squared quietness transform

\begin{equation}
L(x;k)=\frac{1}{1+(x/k)^2}.
\end{equation}

Using created buy orders $C_B$, created sell orders $C_S$, exit units $E$, adverse sell
pressure $P_S$, bid raises $U$, and flipper-attention score $F$, the primitive signals are

\begin{align}
B_H &= H(C_B;3) && \text{buy-order heat},\\
S_Q &= \frac{2}{2+C_S} && \text{absolute sell-order quietness},\\
B_\% &= \frac{C_B+0.5}{C_B+C_S+1} && \text{buy-side order share},\\
P_Q &= \frac{E}{E+P_S+1} && \text{simple pressure quietness},\\
C_Q &= L\!\left(\frac{C_S}{C_B+1};2\right) && \text{sell-creation dominance survival},\\
P_Q^*&=L\!\left(\frac{P_S}{E+1};0.20\right) && \text{strong pressure survival},\\
B_C &= H(U;3) && \text{bid-chase activity}.
\end{align}

\subsection{Flipper attention}

The attention proxy estimates whether the current quoted flip is attractive enough to be
noticed. Let $Q_f=\min(D,S)$ and raw quoted flip profit/hour be

\begin{equation}
\Pi_f=(a_t-b_t)Q_f.
\end{equation}

Then

\begin{align}
F_\Pi&=H(\Pi_f;2{,}000{,}000),\\
F_\rho&=H(\rho_t;0.035),\\
F&=\sqrt{F_\Pi F_\rho}.
\end{align}

This is an internal visibility proxy. It does not query external flipping websites and does
not use the Modern Bazaar flipping rank directly.

\section{Versioned Manipulation Formulas}

The final manipulation score has the common form

\begin{equation}
\boxed{S_{\mathrm{manip}}=
Q_\Pi Q_U Q_M Q_D Q_T Q_O Q_2 Q_R,}
\end{equation}

where $Q_O$ is selected by formula version.

\subsection{Overclocker formula (v1)}

The original empirically successful model strongly rewards buy activity and penalizes
adverse pressure:

\begin{align}
Z_O&=0.30B_H+0.20B_\%+0.15S_Q+0.25P_Q+0.10C_Q,\\
Q_O^{(1)}&=(0.05+0.95Z_O)(0.55+0.45C_Q)(0.10+0.90P_Q^*).
\end{align}

Its strength is practical market control. Its weakness is that a quiet, apparently favorable
market may still fail to attract enough new bidders.

\subsection{Attention formula (v2)}

The Attention model adds direct bidder-chase and flipper-visibility requirements:

\begin{align}
Z_A={}&0.30B_H+0.25B_C+0.15B_\%+0.15S_Q\\
&+0.20P_Q+0.05F+0.05C_Q,\\
Q_O^{(2)}={}&(0.05+0.95Z_A)(0.35+0.65B_C)(0.45+0.55F)\\
&\cdot(0.55+0.45C_Q)(0.10+0.90P_Q^*).
\end{align}

Its strength is evidence of visible competition. Its weakness is that requiring historical
attention can favor markets where the crowd also supplies inventory aggressively.

\subsection{Balanced formula (v3, default)}

Balanced separates attraction from survival before recombining them. Define attention

\begin{equation}
A=0.30B_H+0.25B_C+0.25F+0.20B_\%,
\end{equation}

pressure survival

\begin{equation}
G=0.55P_Q^*+0.25C_Q+0.20P_Q,
\end{equation}

and a broad base

\begin{equation}
Z_B=0.25B_H+0.20B_\%+0.20P_Q+0.15S_Q+0.10B_C+0.10F.
\end{equation}

The order-flow quality is

\begin{equation}
\boxed{
Q_O^{(3)}=(0.05+0.95Z_B)(0.30+0.70A)(0.15+0.85G)
(0.35+0.65P_Q^*)(0.50+0.50C_Q).}
\end{equation}

This is the key quantitative compromise. Attention is valuable, but it cannot compensate
freely for sell pressure because pressure survival enters through several multiplicative
terms. Conversely, a perfectly quiet market is not automatically ranked highly if it lacks
buy heat, bid chasing, and flipper visibility.

\section{Why Balanced Has Worked}

Balanced corresponds closely to the actual execution problem:

\begin{enumerate}
  \item A market must contain enough existing and newly created buyer capacity to provide an
  exit. This is represented by $E$, $C_B$, $N^B$, $V^B$, and $B_C$.
  \item It must attract participants who perceive a profitable spread. This is represented by
  $F$ and historical upward bid movement.
  \item The position must remain controllable while those buyers arrive. This is represented by
  $C_S$, $A^S$, insta-sold units, standing sell depth, and corner size.
  \item The price path must remain plausible and not already look anomalous. This is represented
  by $n_2$ and $R$.
\end{enumerate}

The model is multiplicative because a fatal weakness should not be averaged away by an
unrelated strength. For example, excellent projected profit should not rescue an item with
nearly no exit flow. Balanced softens this principle with nonzero floors so that moderate
imperfections reduce rather than automatically eliminate an opportunity.

\section{Interpretation of Dashboard Outputs}

\begin{longtable}{p{0.25\textwidth}p{0.67\textwidth}}
\toprule
Output & Correct interpretation\\
\midrule
\endhead
Corner cost & Estimated cost of visible plus extrapolated hidden sell-side units.\\
Average buy cost & Corner cost divided by estimated total corner units.\\
Minimum resell & Tax-adjusted break-even price, not a recommended guaranteed exit.\\
Projected profit & Profit if all cornered units exit at the chosen target multiplier.\\
Sell-through & Corner units divided by historical new buy-order units/hour. It is an optimistic
capacity estimate, not a queue simulation.\\
Buy orders/hour & Average observed increases in active buy-order count. It may undercount true creation.\\
Sell orders/hour & Average observed increases in active sell-order count. Lower is generally preferable.\\
Exit units/hour & Estimated units newly added to buy orders.\\
Pressure units/hour & Newly listed sell units plus units insta-sold into bids.\\
Bid raises/hour & Frequency of positive changes in the best bid, independent of jump magnitude.\\
Flip attention & Internal proxy derived from current spread and historical two-sided throughput.\\
Score & Relative ranking utility. It has no direct coin, probability, or expected-return unit.\\
\bottomrule
\end{longtable}

\section{Operational Observability}

The application publishes Micrometer/Actuator metrics to Prometheus. Explicit ingestion
counters include fetched products, persisted snapshots, and poll failures. PostgreSQL metrics
are collected by a dedicated exporter. Grafana reads Prometheus as a provisioned data source.

Operational monitoring should answer four classes of questions:

\begin{itemize}
  \item \textbf{Freshness:} is Hypixel being polled and are new snapshots arriving?
  \item \textbf{Completeness:} are hourly compaction and rolling aggregation keeping up?
  \item \textbf{Capacity:} are database size, connection usage, CPU, memory, and disk healthy?
  \item \textbf{Correctness symptoms:} did opportunity counts collapse, did metrics become flat,
  or did API error rates rise?
\end{itemize}

Prometheus is protected with HTTP Basic authentication at Caddy. Grafana uses its own login.
The API and Actuator endpoints are protected by the application's security configuration.

\section{Statistical and Modeling Limitations}

\subsection{Observation is not an event stream}

The API provides periodic market states, not every order creation, cancellation, fill, or
replacement. Metrics derived from state differences are therefore interval-censored. Events
that cancel each other between polls cannot be reconstructed exactly.

\subsection{Hidden depth is estimated}

Only part of the order book is visible. The corner estimator extrapolates average units/order
and applies a price premium, but a single large hidden order or sharply rising hidden price
ladder can make actual acquisition cost much higher.

\subsection{Averages mix market regimes}

The 48-hour manipulation window stabilizes rankings but reacts slowly to sudden changes.
Maintenance, game updates, weekends, creator attention, or an active manipulator can shift the
current regime away from the historical mean.

\subsection{Exit flow is not price-conditioned}

$E$ measures new buy-order units at historical prices. The current model does not estimate

\begin{equation}
\Pr(\text{new bid price}\ge p_T)
\end{equation}

or model the probability that another seller consumes those units first. This is why displayed
sell-through can be materially faster than realized liquidation.

\subsection{Bid raises are sampling-sensitive}

The count $U_h$ depends on polling frequency and treats a minimal increase like a major move.
The stored magnitude $\Delta_h^+$ could eventually distinguish economically meaningful bidder
competition from noise.

\subsection{Scores are calibrated rankings, not probabilities}

Neither strategy score is a probability of success. Coefficients and half-saturation constants
encode practical preferences and observed behavior. Their strongest validation is comparative:
better-ranked items should produce better realized outcomes on average under comparable execution.

\section{Validation Framework}

The next quantitative step should preserve the successful Balanced formula and evaluate it
against a trade journal. For trade $j$, record at decision time:

\begin{equation*}
x_j=(\widehat U,\widehat C,D,S,C_B,C_S,E,P_S,U,F,R,n_2,T_E,S_{\mathrm{manip}})
\end{equation*}

and after execution:

\begin{equation*}
y_j=(C_j^{\mathrm{actual}},T_j^{\mathrm{exit}},\Pi_j^{\mathrm{realized}},
\mathrm{drawdown}_j,\mathrm{success}_j).
\end{equation*}

Recommended validation statistics include:

\begin{align}
\text{Corner cost error}_j&=\frac{C_j^{\mathrm{actual}}-\widehat C_j}{\widehat C_j},\\
\text{Exit-time error}_j&=\frac{T_j^{\mathrm{exit}}-T_{E,j}}{T_{E,j}},\\
\text{Profit realization}_j&=\frac{\Pi_j^{\mathrm{realized}}}{\widehat\Pi_j}.
\end{align}

Rank quality can be measured using Spearman correlation between score and realized profit,
precision among the top $k$ opportunities, median drawdown by score decile, and calibration
curves for any later success-probability model.

An especially useful design is an immutable \emph{decision snapshot}: store exactly the
features and formula version shown when a trade is selected. This prevents later data updates
from contaminating historical backtests.

\section{Path Toward Simulation and Machine Learning}

A future learning system should not begin by replacing the scorer. Balanced can serve as a
strong policy prior and benchmark.

\subsection{Replay environment}

At decision time $t$, the state may contain live book features, rolling windows, risk, item
metadata, and current inventory. An action specifies whether to enter, capital allocated,
target price, wall configuration, and exit policy. Reward should be realized net profit minus
explicit penalties for drawdown, time in position, and unliquidated inventory:

\begin{equation}
r_t=\Delta\mathrm{coins}_t
-\lambda_D\mathrm{drawdown}_t
-\lambda_T\mathrm{capital\ time}_t
-\lambda_I\mathrm{inventory}_t.
\end{equation}

The replay engine must enforce causality: the model may use only information available at time
$t$. Random train/test splitting is inappropriate for market data; evaluation should use
walk-forward time splits.

\subsection{Recommended modeling sequence}

\begin{enumerate}
  \item Predict realized exit time and adverse sell pressure as supervised targets.
  \item Predict probability of reaching several return thresholds within 1, 2, and 6 hours.
  \item Use those calibrated predictions to rerank Balanced candidates.
  \item Introduce policy optimization only after the replay environment reproduces actual
  historical trades with acceptable error.
\end{enumerate}

This sequence is easier to debug than immediately training a reinforcement-learning agent and
provides measurable improvements at every stage.

\section{Recommended Quantitative Improvements}

The following changes offer the highest information gain without discarding the empirically
successful Balanced model:

\begin{enumerate}
  \item \textbf{Outcome logging.} Record actual entry cost, fills, new orders, competing sells,
  exit time, realized profit, and formula version.
  \item \textbf{Multi-window manipulation features.} Keep the 48-hour baseline, but expose 1-hour
  and 6-hour ratios to detect regime changes rather than replacing the baseline outright.
  \item \textbf{Metric confidence.} Attach observation count, missing-hour ratio, and sample
  freshness to every rolling feature.
  \item \textbf{Pressure decomposition.} Keep new sell listings and insta-sells separate in
  analysis so their independent effects can be estimated from outcomes.
  \item \textbf{Price-conditioned exits.} Estimate the distribution of newly created bid prices,
  not only their total units.
  \item \textbf{Magnitude-aware bidder chase.} Combine $U_h$ with normalized $\Delta_h^+$ while
  retaining the present count as a stable feature.
  \item \textbf{Robust aggregation.} Compare arithmetic means with medians, trimmed means, and
  exponentially weighted averages during offline evaluation.
\end{enumerate}

These are research directions, not immediate formula edits. The present Balanced model should
remain versioned and reproducible while evidence is collected.

\section{Conclusion}

Modern Bazaar is best understood as a layered quantitative decision system. It does not merely
sort products by spread. It observes the market repeatedly, compresses those observations into
hourly behavior, compares current prices with historical references, estimates feasible trade
size, and ranks opportunities using explicit economic constraints.

The Balanced manipulation formula is strong because it models the central tension directly:
a profitable-looking market needs enough attention to create buyers, but not so much adverse
supply that the position becomes uncontrollable. Its current success is plausible from both
the mathematics and observed execution. The system's main uncertainties lie upstream in
partial order-book visibility and state-difference proxies, and downstream in the absence of
price-conditioned exit probabilities.

The correct next phase is measurement rather than uncontrolled coefficient tuning. A reliable
decision-time feature log and realized-trade journal would transform the scorer from an
empirically promising ranking into a system that can be calibrated, backtested, and eventually
used as the foundation for simulation and machine learning.

\clearpage
\appendix
\section{Principal Constants}

\begin{longtable}{p{0.38\textwidth}p{0.14\textwidth}p{0.36\textwidth}}
\toprule
Constant & Value & Interpretation\\
\midrule
\endhead
Default Bazaar sale tax & 1.125\% & Deducted from manipulation sale proceeds\\
Maximum demand/supply ratio & 5.0 & Prevents unbounded ratios near zero supply\\
Minimum demand & 1 unit/h & Manipulation hard gate\\
Maximum exit time & 24 h & Manipulation hard gate\\
Maximum bid doublings & 6 & Manipulation hard gate\\
Risk hard gate & 0.85 & Excludes highly atypical regimes\\
Demand half-saturation & 10 units/h & Common demand quality\\
Exit-time half-saturation & 3 h & Common exit quality\\
Created-buy half-saturation & 3 orders/h & Order-flow buy heat\\
Bid-raise half-saturation & 3 raises/h & Bidder-chase confidence\\
Sell-order half-saturation & 2 orders/h & Sell quietness\\
Pressure-ratio half-saturation & 0.20 & Strong adverse-pressure penalty\\
Corner-size half-saturation & 10,000 units & Practical inventory preference\\
Active sell-order half-saturation & 60 & Standing control\\
Active buy-order half-saturation & 120 & Standing buyer depth\\
Flip-attention profit half-saturation & 2,000,000 coins/h & Internal visibility proxy\\
Flip-attention spread half-saturation & 3.5\% & Internal visibility proxy\\
Default max current item price & 1,500,000 coins & List filter\\
Default automatic profit floor & 10\% of budget & Capped at 50 million coins\\
\bottomrule
\end{longtable}

\section{Notation Summary}

\begin{longtable}{p{0.20\textwidth}p{0.72\textwidth}}
\toprule
Symbol & Definition\\
\midrule
\endhead
$a_t,b_t$ & Current ask and bid\\
$D,S$ & Average insta-buy demand and insta-sell supply, units/hour\\
$C_B,C_S$ & Observed created buy/sell order proxies, orders/hour\\
$E$ & Newly added buy-order units/hour, used as exit capacity\\
$P_S$ & Added sell-order units plus insta-sold units/hour\\
$U$ & Positive best-bid movements/hour\\
$F$ & Internal flipper-attention score in $[0,1]$\\
$R$ & Price-deviation risk score in $[0,1]$\\
$\widehat U,\widehat C$ & Estimated corner units and cost\\
$p_{\mathrm{BE}},p_T,p_W$ & Break-even, target buy-order, and sell-wall prices\\
$T_E$ & Estimated position exit time\\
$Q_O^{(1)},Q_O^{(2)},Q_O^{(3)}$ & Overclocker, Attention, and Balanced order-flow quality\\
\bottomrule
\end{longtable}

\vfill
\begin{center}
\small\color{textgray}
Prepared for the Modern Bazaar project.\\
Author: Pedro Silva.
\end{center}

\end{document}
